### 2014-03-14 src/related.Rnw
Fixing the pointed out issues: do/faster/fewer/smarter
Fix unintented %'s
fix conflict

\section{Related Work}
\label{sec:related}
In this section we summarize the related work. There have been
different approaches to reduce the cost of mutation analysis.
These were categorized by Offutt and Untch~\cite{offutt2001mutation}
into three approaches: Do \textit{fewer}, \textit{smarter}, \textit{faster}.
The fewer approaches includes selective mutation and mutant sampling while
weak mutation, parallelization of mutation analysis, space time trade offs
are grouped under the umbrella of \textit{do smarter}. Finally
\textit{do faster} approaches include byte code based mutation analysis
systems like PIT, and similar binary patching methods.

The idea of using a subset of mutants was born along with the mutation analysis
itself. Budd~\cite{budd1980mutation} and Acree~\cite{Acree1980} showed that
even 10\% sampling can achieve 99\% accuracy for the final score.

It was further investigated by Mathur~\cite{mathur1991performance},
Wong et al.~\cite{wong1993mutation,wong1995reducing}, and
Offutt et al.~\cite{offutt1993experimental} using the Mothra~\cite{Mothra}
mutation operators for Fortran. Mathur~\cite{mathur1991performance,wong1995reducing}
suggested constrained mutation where in only two mutation operators were used which
were felt to be better than using the entire set.

@@

A number of studies in the past have looked at the relative merits of operator
selection and random sampling criteria, starting with Wong and Mathur in
1995~\cite{wong1995reducing}. They compared x\% selection of each mutant type
with operator selection of just two mutation operators, and finds that both
achieved similar accuracy and reduction (80\%). This study was conducted on
five small programs in C and Fortran.

Some studies have tried to find set of \emph{sufficient mutation operators} that
while reducing the cost of mutations, maintains the correlation with the full
mutation score. Offutt~\cite{offutt1993experimental} suggested n-selective
approach which advocates step by step removal of mutation operators that produced
the largest number of mutants.

Mresa et al.\cite{mresa1999efficiency} used the cost of detection of mutants as
a means of selection, and uses it to define a set of operators. They find
that if very high mutation score close to 100\% is required, x\% selective
mutation is better than operator selection, and conversely for less stringent
scores, operator selection would be better if cost of mutant is considered.

Barbosa et. al.\cite{barbosa2001toward} provides a set of guidelines for selecting
such mutation operators. Namin et al.\cite{namin2006finding,siami2008sufficient}
formulate this problem as a variable reduction problem, and apply statistical
approaches. They found a subset of 28 operators out of 108 operators as the sufficient
operators.

Using only the statement deletion operator was first suggested by
Untch~\cite{untch2009onreduced}, who found that it correlated ($R^2 = 0.97$) with the
full mutation score better than other operator selection methods, while generating the
least number of mutants.  This was further reinforced by Deng et al.~\cite{deng2013empirical}
who defined deletion for different language elements, and found that an accuracy of 92\% is
achieved while reducing the mutants by 80\%.

Zhang et al.~\cite{zhang2010operator} compares operators based mutant selection in
~\cite{barbosa2001toward,siami2008sufficient,offutt1996anexperimental} to random mutant selection.
They find that none of these selection techniques are superior to random selection, with same number of
mutants. They also find that equal mutation sampling is more effective for larger subjects compared to
equal mutagen sampling and the reverse is true for smaller subjects.

Recently, Zhang et al.~\cite{zhang2013ase} confirmed that sampling as few as 5\% mutants
was sufficient for a very correlation (99\%) with the full mutation score, while sampling even
fewer mutants has good potential for retaining high accuracy. They investigate 8 sampling
strategies on top of operator based mutant selection and find that sampling strategies
based on program components (based on methods) performed best.

@@

This work is closely related to Zhang et al.~\cite{zhang2013ase}. We extend the scope of
their study with much wider range of mutation selection and we experimented them on much more
real-world projects.

>>>>

\section{Related Work}
\label{sec:related}
There are several approaches to reducing the cost of mutation analysis.
These were categorized by Offutt and Untch~\cite{offutt2001mutation}
into three approaches: do \textit{fewer}, \textit{smarter}, or \textit{faster}.
The fewer approaches includes selective mutation and mutant sampling;
weak mutation, parallelization of mutation analysis, and space/time trade-offs
are grouped under the umbrella of \textit{do smarter}. Finally
\textit{do faster} approaches include mutant schema generation methods,
code patching techniques, and byte code based mutation analysis systems like PIT.

The idea of using a subset of mutants was conceived along with
mutation analysis itself. Budd~\cite{budd1980mutation} and
Acree~\cite{Acree1980} showed that even 10\% sampling can achieve 99\%
accuracy for the final score.  The idea was further investigated by
Mathur~\cite{mathur1991performance}, Wong et
al.~\cite{wong1993mutation,wong1995reducing}, and Offutt et
al.~\cite{offutt1993experimental} using the Mothra~\cite{Mothra}
mutation operators for
Fortran. Mathur~\cite{mathur1991performance,wong1995reducing}
suggested constrained mutation where only two mutation operators
were used.%, which were felt to be better than using the entire set.

@@

A number of studies in the past have looked at the relative merits of operator
selection and random sampling criteria, starting with Wong and Mathur in
1995~\cite{wong1995reducing}. They compared x\% selection of each mutant type
with operator selection using just two mutation operators, and found that both
achieved similar accuracy and reduction (80\%). This study was conducted on
five small programs in C and Fortran.

Some studies have tried to find set of \emph{sufficient mutation
operators} that reduce the cost of mutation but maintain correlation
with the full mutation score. Offutt~\cite{offutt1993experimental}
suggested an $n$-selective approach with step-by-step removal of
mutation operators that produced the largest number of mutants.

Mresa et al.\cite{mresa1999efficiency} used the cost of detection of
mutants as a means of selection to define a set of operators. They
found that if very high mutation score (close to 100\%) is required,
x\% selective mutation is better than operator selection, and,
conversely, for lower scores, operator selection would be better if
the cost of mutants is considered.

Barbosa et. al.\cite{barbosa2001toward} provide a set of guidelines
for selecting such mutation operators. Namin et
al.\cite{namin2006finding,siami2008sufficient} formulate the problem
as a variable reduction problem, and apply statistical
approaches. They found a subset of 28 operators out of 108 operators that are
sufficient.

Using only the statement deletion operator was first suggested by
Untch~\cite{untch2009onreduced}, who found that it correlated ($R^2 =
0.97$) with the full mutation score better than other operator
selection methods, while generating the smallest number of mutants.
This was further reinforced by Deng et al.~\cite{deng2013empirical}
who defined deletion for different language elements, and found that
an accuracy of 92\% is achieved while reducing the number of mutants
by 80\%.

Zhang et al.~\cite{zhang2010operator} compares operators based mutant
selection techniques proposed in a set of
papers~\cite{barbosa2001toward,siami2008sufficient,offutt1996anexperimental}
to random mutant sampling.  They find that none of the selection
techniques are superior to random sampling, with the same number of
mutants. They also find that equal mutation sampling is more effective
for larger subjects compared to equal mutagen sampling and the reverse
is true for smaller subjects. {\bf ADG:  not having defined mutagen/mtuation sampling this is not easy for most readers to understand.  also we switch between "sampling" and "random selection" a lot, I tried to make consistent.}

Recently, Zhang et al.~\cite{zhang2013ase} confirmed that sampling as
few as 5\% of mutants was sufficient for a very high correlation
(99\%) with full mutation score, while sampling even fewer mutants has
good potential for retaining high accuracy. They investigated 8
sampling strategies on top of operator-based mutant selection and
found that sampling strategies based on program components (methods in
particular) performed best.

@@

Our work is most closely related to that of Zhang et
al.~\cite{zhang2013ase}. We extend the scope of their study with a
much wider range of mutation approches and base our results on a large
set of real-world projects.
